---
title: "ML_Project_Pablo_Leon"
author: "Pablo Leon (p.leon@ieee.org)"
date: "18 de agosto de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assigment: Prediction Assignment Writeup

In this project, our goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants.


## Executive Summary

Our preferred prediction model is a stacked one, using generalizaed lineal (GLM), linear discriminant (LDA),
and boosting (GBM).

From the ytrain data we discarded those recvord marked as new_window = "yes", those records represent
statistics over a time window of simple metrics (new_window="no"). The reason
for this is that the Test dataset does not contains that kind of records.
Several columns ("kurtosis_roll_dumbbell", "max_roll_forearm", "amplitude_yaw_forearm"
, "kurtosis_yaw_dumbbell") only make sense for those omitted recors, so we discard this columns too.

In several cases, particularly on class "A" captures, it seems that for the first few seconds
the user is not performing the exercise, as we can count around 10 cycles on some variables
starting in the midst of the recording.

That observation allows us to trim the training data discarding the first seconds of the recording
in order to avoid training with data before the exercise is performed.

Nevertheless we didn't needed to do that in order to obtain good quality predictions.

On preprocessing we :
* found none zero nor near-zero variance variables, 
* found none variable wich is a linear combination of other variables
* several variables with high linear correlation.

We checked principal component transformation, but found that transformation tend to emphasize
difference between users rather than differences between classes (the data feed to the transformation 
did not included the username).  

So we avoided the PCA transformation, an used the raw data, then excluding higly correlated variables.

We used a 8-fold cross-validation to estimate in-training accuracy.

Our prefered model uses stacking using LDA, GLM GBM models and the user_name variable, since we are
convinced that particularities of the captured data make sense mostly between data from the same user.

Other models that completly ignore the user_name variable produced weaker predictions.

Our preferred model have an inner 8-fold accuracy of 0.998 (Kappa of 0.99595).




## Initialize & Load Data
```{r echo=FALSE, messages=FALSE, warnings=FALSE}
suppressPackageStartupMessages({
  library(AppliedPredictiveModeling)
  library(caret)
  library(ElemStatLearn)
  library(pgmm)
  library(rpart)
  library(gbm)
  library(forecast)
  library(e1071)
  
  
  library(caret)
  
  library(lubridate)
  library(tibble)
  library(readr)
  library(tidyr)
  library(dplyr)
  library(skimr)
  library(ggplot2)
  library(gridExtra)
  
  library(doParallel)
})
```


```{r echo=FALSE}
dfTest_Read <- read_csv("../data/pml-testing.csv"
                         ,col_types = cols(
                           X1 = col_integer(),
                           user_name = col_character(),
                           raw_timestamp_part_1 = col_integer(),
                           raw_timestamp_part_2 = col_integer(),
                           cvtd_timestamp = col_character(),
                           new_window = col_character(),
                           num_window = col_integer(),
                           roll_belt = col_double(),
                           pitch_belt = col_double(),
                           yaw_belt = col_double(),
                           total_accel_belt = col_integer(),
                           kurtosis_roll_belt = col_character(),
                           kurtosis_picth_belt = col_character(),
                           kurtosis_yaw_belt = col_character(),
                           skewness_roll_belt = col_character(),
                           skewness_roll_belt.1 = col_character(),
                           skewness_yaw_belt = col_character(),
                           max_roll_belt = col_double(),
                           max_picth_belt = col_integer(),
                           max_yaw_belt = col_character(),
                           min_roll_belt = col_double(),
                           min_pitch_belt = col_integer(),
                           min_yaw_belt = col_character(),
                           amplitude_roll_belt = col_double(),
                           amplitude_pitch_belt = col_integer(),
                           amplitude_yaw_belt = col_character(),
                           var_total_accel_belt = col_double(),
                           avg_roll_belt = col_double(),
                           stddev_roll_belt = col_double(),
                           var_roll_belt = col_double(),
                           avg_pitch_belt = col_double(),
                           stddev_pitch_belt = col_double(),
                           var_pitch_belt = col_double(),
                           avg_yaw_belt = col_double(),
                           stddev_yaw_belt = col_double(),
                           var_yaw_belt = col_double(),
                           gyros_belt_x = col_double(),
                           gyros_belt_y = col_double(),
                           gyros_belt_z = col_double(),
                           accel_belt_x = col_integer(),
                           accel_belt_y = col_integer(),
                           accel_belt_z = col_integer(),
                           magnet_belt_x = col_integer(),
                           magnet_belt_y = col_integer(),
                           magnet_belt_z = col_integer(),
                           roll_arm = col_double(),
                           pitch_arm = col_double(),
                           yaw_arm = col_double(),
                           total_accel_arm = col_integer(),
                           var_accel_arm = col_double(),
                           avg_roll_arm = col_double(),
                           stddev_roll_arm = col_double(),
                           var_roll_arm = col_double(),
                           avg_pitch_arm = col_double(),
                           stddev_pitch_arm = col_double(),
                           var_pitch_arm = col_double(),
                           avg_yaw_arm = col_double(),
                           stddev_yaw_arm = col_double(),
                           var_yaw_arm = col_double(),
                           gyros_arm_x = col_double(),
                           gyros_arm_y = col_double(),
                           gyros_arm_z = col_double(),
                           accel_arm_x = col_integer(),
                           accel_arm_y = col_integer(),
                           accel_arm_z = col_integer(),
                           magnet_arm_x = col_integer(),
                           magnet_arm_y = col_integer(),
                           magnet_arm_z = col_integer(),
                           kurtosis_roll_arm = col_character(),
                           kurtosis_picth_arm = col_character(),
                           kurtosis_yaw_arm = col_character(),
                           skewness_roll_arm = col_character(),
                           skewness_pitch_arm = col_character(),
                           skewness_yaw_arm = col_character(),
                           max_roll_arm = col_double(),
                           max_picth_arm = col_double(),
                           max_yaw_arm = col_integer(),
                           min_roll_arm = col_double(),
                           min_pitch_arm = col_double(),
                           min_yaw_arm = col_integer(),
                           amplitude_roll_arm = col_double(),
                           amplitude_pitch_arm = col_double(),
                           amplitude_yaw_arm = col_integer(),
                           roll_dumbbell = col_double(),
                           pitch_dumbbell = col_double(),
                           yaw_dumbbell = col_double(),
                           kurtosis_roll_dumbbell = col_character(),
                           kurtosis_picth_dumbbell = col_character(),
                           kurtosis_yaw_dumbbell = col_character(),
                           skewness_roll_dumbbell = col_character(),
                           skewness_pitch_dumbbell = col_character(),
                           skewness_yaw_dumbbell = col_character(),
                           max_roll_dumbbell = col_double(),
                           max_picth_dumbbell = col_double(),
                           max_yaw_dumbbell = col_character(),
                           min_roll_dumbbell = col_double(),
                           min_pitch_dumbbell = col_double(),
                           min_yaw_dumbbell = col_character(),
                           amplitude_roll_dumbbell = col_double(),
                           amplitude_pitch_dumbbell = col_double(),
                           amplitude_yaw_dumbbell = col_character(),
                           total_accel_dumbbell = col_integer(),
                           var_accel_dumbbell = col_double(),
                           avg_roll_dumbbell = col_double(),
                           stddev_roll_dumbbell = col_double(),
                           var_roll_dumbbell = col_double(),
                           avg_pitch_dumbbell = col_double(),
                           stddev_pitch_dumbbell = col_double(),
                           var_pitch_dumbbell = col_double(),
                           avg_yaw_dumbbell = col_double(),
                           stddev_yaw_dumbbell = col_double(),
                           var_yaw_dumbbell = col_double(),
                           gyros_dumbbell_x = col_double(),
                           gyros_dumbbell_y = col_double(),
                           gyros_dumbbell_z = col_double(),
                           accel_dumbbell_x = col_integer(),
                           accel_dumbbell_y = col_integer(),
                           accel_dumbbell_z = col_integer(),
                           magnet_dumbbell_x = col_integer(),
                           magnet_dumbbell_y = col_integer(),
                           magnet_dumbbell_z = col_double(),
                           roll_forearm = col_double(),
                           pitch_forearm = col_double(),
                           yaw_forearm = col_double(),
                           kurtosis_roll_forearm = col_character(),
                           kurtosis_picth_forearm = col_character(),
                           kurtosis_yaw_forearm = col_character(),
                           skewness_roll_forearm = col_character(),
                           skewness_pitch_forearm = col_character(),
                           skewness_yaw_forearm = col_character(),
                           max_roll_forearm = col_double(),
                           max_picth_forearm = col_double(),
                           max_yaw_forearm = col_character(),
                           min_roll_forearm = col_double(),
                           min_pitch_forearm = col_double(),
                           min_yaw_forearm = col_character(),
                           amplitude_roll_forearm = col_double(),
                           amplitude_pitch_forearm = col_double(),
                           amplitude_yaw_forearm = col_character(),
                           total_accel_forearm = col_integer(),
                           var_accel_forearm = col_double(),
                           avg_roll_forearm = col_double(),
                           stddev_roll_forearm = col_double(),
                           var_roll_forearm = col_double(),
                           avg_pitch_forearm = col_double(),
                           stddev_pitch_forearm = col_double(),
                           var_pitch_forearm = col_double(),
                           avg_yaw_forearm = col_double(),
                           stddev_yaw_forearm = col_double(),
                           var_yaw_forearm = col_double(),
                           gyros_forearm_x = col_double(),
                           gyros_forearm_y = col_double(),
                           gyros_forearm_z = col_double(),
                           accel_forearm_x = col_integer(),
                           accel_forearm_y = col_integer(),
                           accel_forearm_z = col_integer(),
                           magnet_forearm_x = col_integer(),
                           magnet_forearm_y = col_double(),
                           magnet_forearm_z = col_double(),
                           problem_id = col_character()
                         ))
                         
vNewWindow <- unique(dfTest_Read$new_window)

```



```{r echo=FALSE}
dfTrain_Read <- read_csv("../data/pml-training.csv"
                         ,col_types = cols(
                           X1 = col_integer(),
                           user_name = col_character(),
                           raw_timestamp_part_1 = col_integer(),
                           raw_timestamp_part_2 = col_integer(),
                           cvtd_timestamp = col_character(),
                           new_window = col_character(),
                           num_window = col_integer(),
                           roll_belt = col_double(),
                           pitch_belt = col_double(),
                           yaw_belt = col_double(),
                           total_accel_belt = col_integer(),
                           kurtosis_roll_belt = col_character(),
                           kurtosis_picth_belt = col_character(),
                           kurtosis_yaw_belt = col_character(),
                           skewness_roll_belt = col_character(),
                           skewness_roll_belt.1 = col_character(),
                           skewness_yaw_belt = col_character(),
                           max_roll_belt = col_double(),
                           max_picth_belt = col_integer(),
                           max_yaw_belt = col_character(),
                           min_roll_belt = col_double(),
                           min_pitch_belt = col_integer(),
                           min_yaw_belt = col_character(),
                           amplitude_roll_belt = col_double(),
                           amplitude_pitch_belt = col_integer(),
                           amplitude_yaw_belt = col_character(),
                           var_total_accel_belt = col_double(),
                           avg_roll_belt = col_double(),
                           stddev_roll_belt = col_double(),
                           var_roll_belt = col_double(),
                           avg_pitch_belt = col_double(),
                           stddev_pitch_belt = col_double(),
                           var_pitch_belt = col_double(),
                           avg_yaw_belt = col_double(),
                           stddev_yaw_belt = col_double(),
                           var_yaw_belt = col_double(),
                           gyros_belt_x = col_double(),
                           gyros_belt_y = col_double(),
                           gyros_belt_z = col_double(),
                           accel_belt_x = col_integer(),
                           accel_belt_y = col_integer(),
                           accel_belt_z = col_integer(),
                           magnet_belt_x = col_integer(),
                           magnet_belt_y = col_integer(),
                           magnet_belt_z = col_integer(),
                           roll_arm = col_double(),
                           pitch_arm = col_double(),
                           yaw_arm = col_double(),
                           total_accel_arm = col_integer(),
                           var_accel_arm = col_double(),
                           avg_roll_arm = col_double(),
                           stddev_roll_arm = col_double(),
                           var_roll_arm = col_double(),
                           avg_pitch_arm = col_double(),
                           stddev_pitch_arm = col_double(),
                           var_pitch_arm = col_double(),
                           avg_yaw_arm = col_double(),
                           stddev_yaw_arm = col_double(),
                           var_yaw_arm = col_double(),
                           gyros_arm_x = col_double(),
                           gyros_arm_y = col_double(),
                           gyros_arm_z = col_double(),
                           accel_arm_x = col_integer(),
                           accel_arm_y = col_integer(),
                           accel_arm_z = col_integer(),
                           magnet_arm_x = col_integer(),
                           magnet_arm_y = col_integer(),
                           magnet_arm_z = col_integer(),
                           kurtosis_roll_arm = col_character(),
                           kurtosis_picth_arm = col_character(),
                           kurtosis_yaw_arm = col_character(),
                           skewness_roll_arm = col_character(),
                           skewness_pitch_arm = col_character(),
                           skewness_yaw_arm = col_character(),
                           max_roll_arm = col_double(),
                           max_picth_arm = col_double(),
                           max_yaw_arm = col_integer(),
                           min_roll_arm = col_double(),
                           min_pitch_arm = col_double(),
                           min_yaw_arm = col_integer(),
                           amplitude_roll_arm = col_double(),
                           amplitude_pitch_arm = col_double(),
                           amplitude_yaw_arm = col_integer(),
                           roll_dumbbell = col_double(),
                           pitch_dumbbell = col_double(),
                           yaw_dumbbell = col_double(),
                           kurtosis_roll_dumbbell = col_character(),
                           kurtosis_picth_dumbbell = col_character(),
                           kurtosis_yaw_dumbbell = col_character(),
                           skewness_roll_dumbbell = col_character(),
                           skewness_pitch_dumbbell = col_character(),
                           skewness_yaw_dumbbell = col_character(),
                           max_roll_dumbbell = col_double(),
                           max_picth_dumbbell = col_double(),
                           max_yaw_dumbbell = col_character(),
                           min_roll_dumbbell = col_double(),
                           min_pitch_dumbbell = col_double(),
                           min_yaw_dumbbell = col_character(),
                           amplitude_roll_dumbbell = col_double(),
                           amplitude_pitch_dumbbell = col_double(),
                           amplitude_yaw_dumbbell = col_character(),
                           total_accel_dumbbell = col_integer(),
                           var_accel_dumbbell = col_double(),
                           avg_roll_dumbbell = col_double(),
                           stddev_roll_dumbbell = col_double(),
                           var_roll_dumbbell = col_double(),
                           avg_pitch_dumbbell = col_double(),
                           stddev_pitch_dumbbell = col_double(),
                           var_pitch_dumbbell = col_double(),
                           avg_yaw_dumbbell = col_double(),
                           stddev_yaw_dumbbell = col_double(),
                           var_yaw_dumbbell = col_double(),
                           gyros_dumbbell_x = col_double(),
                           gyros_dumbbell_y = col_double(),
                           gyros_dumbbell_z = col_double(),
                           accel_dumbbell_x = col_integer(),
                           accel_dumbbell_y = col_integer(),
                           accel_dumbbell_z = col_integer(),
                           magnet_dumbbell_x = col_integer(),
                           magnet_dumbbell_y = col_integer(),
                           magnet_dumbbell_z = col_double(),
                           roll_forearm = col_double(),
                           pitch_forearm = col_double(),
                           yaw_forearm = col_double(),
                           kurtosis_roll_forearm = col_character(),
                           kurtosis_picth_forearm = col_character(),
                           kurtosis_yaw_forearm = col_character(),
                           skewness_roll_forearm = col_character(),
                           skewness_pitch_forearm = col_character(),
                           skewness_yaw_forearm = col_character(),
                           max_roll_forearm = col_double(),
                           max_picth_forearm = col_double(),
                           max_yaw_forearm = col_character(),
                           min_roll_forearm = col_double(),
                           min_pitch_forearm = col_double(),
                           min_yaw_forearm = col_character(),
                           amplitude_roll_forearm = col_double(),
                           amplitude_pitch_forearm = col_double(),
                           amplitude_yaw_forearm = col_character(),
                           total_accel_forearm = col_integer(),
                           var_accel_forearm = col_double(),
                           avg_roll_forearm = col_double(),
                           stddev_roll_forearm = col_double(),
                           var_roll_forearm = col_double(),
                           avg_pitch_forearm = col_double(),
                           stddev_pitch_forearm = col_double(),
                           var_pitch_forearm = col_double(),
                           avg_yaw_forearm = col_double(),
                           stddev_yaw_forearm = col_double(),
                           var_yaw_forearm = col_double(),
                           gyros_forearm_x = col_double(),
                           gyros_forearm_y = col_double(),
                           gyros_forearm_z = col_double(),
                           accel_forearm_x = col_integer(),
                           accel_forearm_y = col_integer(),
                           accel_forearm_z = col_integer(),
                           magnet_forearm_x = col_integer(),
                           magnet_forearm_y = col_double(),
                           magnet_forearm_z = col_double(),
                           classe = col_character()
                         ))

dfCheck <- dfTrain_Read %>%
  select(raw_timestamp_part_1, num_window, user_name) %>%
  unique()

```



```{r echo=FALSE}
dfTrain <- dfTrain_Read %>%
  filter(new_window %in% vNewWindow) %>%
  select(-X1, -new_window, -cvtd_timestamp) %>%
  mutate(  
    correct = factor( if_else(classe == "A", "Yes", "No") )
    ,classe = factor(classe)
    ,user_name = factor(user_name)
    ) %>%
  select(correct, classe
         ,user_name, num_window
         ,raw_timestamp_part_1, raw_timestamp_part_2
         ,everything()) %>%
  group_by(user_name, classe) %>%
  mutate( 
    rel_win = dense_rank(num_window)
    ,ts = dense_rank(raw_timestamp_part_1) + raw_timestamp_part_2/1000000
    ) %>%
  ungroup()


vNames_Train <- names(dfTrain)
nTrain <- nrow(dfTrain)

for (j in rev(seq_along(dfTrain))) {
  v  <- dfTrain[[j]]
  if (sum(is.na(v)) == nTrain) {
    # print(sprintf("field is NA(%d): %s", j, vNames_Train[j]))
    dfTrain[[j]] <- NULL
  }
}

# table(dfTrain$classe, dfTrain$user_name, useNA="ifany")
# table(dfTrain$classe, dfTrain$correct, useNA="ifany")


dfTrain_Y <- dfTrain %>%
  select(correct, classe)

dfTrain_X <- dfTrain %>%
  select(-correct, -classe
         ,-rel_win, -ts
         )

```



## Explore


```{r echo=FALSE}

# > toString(names(dfTrain) %>% sort() %>% .[grepl("dumbbell", .)])
# [1] "accel_dumbbell_x, accel_dumbbell_y, accel_dumbbell_z
# , gyros_dumbbell_x, gyros_dumbbell_y, gyros_dumbbell_z
# , magnet_dumbbell_x, magnet_dumbbell_y, magnet_dumbbell_z
# , pitch_dumbbell, roll_dumbbell, yaw_dumbbell
# , total_accel_dumbbell"


dfTrain_Long <- dfTrain %>%
  ungroup()  %>%
  gather(key = "var", value = "val"
         ,total_accel_belt
         ,total_accel_arm
         ,total_accel_dumbbell
         ,total_accel_forearm
         ,roll_belt, pitch_belt, yaw_belt
         ,gyros_belt_x, gyros_belt_y, gyros_belt_z
         ,accel_belt_x, accel_belt_y, accel_belt_z
         ,magnet_belt_x, magnet_belt_y, magnet_belt_z
         ,roll_arm, pitch_arm, yaw_arm
         ,gyros_arm_x, gyros_arm_y, gyros_arm_z
         ,accel_arm_x, accel_arm_y, accel_arm_z
         ,magnet_arm_x, magnet_arm_y, magnet_arm_z
         ,roll_dumbbell, pitch_dumbbell, yaw_dumbbell
         ,gyros_dumbbell_x, gyros_dumbbell_y, gyros_dumbbell_z
         ,accel_dumbbell_x, accel_dumbbell_y, accel_dumbbell_z
         ,magnet_dumbbell_x, magnet_dumbbell_y, magnet_dumbbell_z
         ,roll_forearm, pitch_forearm, yaw_forearm
         ,gyros_forearm_x, gyros_forearm_y, gyros_forearm_z
         ,accel_forearm_x, accel_forearm_y, accel_forearm_z
         ,magnet_forearm_x, magnet_forearm_y, magnet_forearm_z
         ) %>%
  mutate( var   = factor(var) )

```




```{r eval=FALSE, echo=FALSE}

vUserNames <- levels(dfTrain$user_name)

dfAux <- dfTrain_Long %>%
  filter( user_name == vUserNames[1] ) %>%
  filter( var %in% c("total_accel_belt", "total_accel_arm", "total_accel_dumbbell", "total_accel_forearm" ))


pltChart <- ggplot(dfAux
               ,aes(x=ts, y=val, color=var)) +
    geom_point(shape=20) +
    facet_grid( classe ~ . )

pltChart
```



The following chart seems to indicate that on class "A" exercises, the first seconds the users are not performing 
the exercise, since there are around 10 cycles of acceleration starting in the midst of the recording.


```{r echo=TRUE}

dfAux <- dfTrain_Long %>%
  filter( classe == "A") %>%
  filter( var %in% c("total_accel_belt", "total_accel_arm", "total_accel_dumbbell", "total_accel_forearm" ))


pltChart <- ggplot(dfAux
               ,aes(x=ts, y=val, color=var)) +
    geom_point(shape=20) +
    facet_grid( user_name ~ . )

pltChart
```



```{r eval=FALSE, echo=FALSE}

dfAux <- dfTrain_Long %>%
  filter( classe == "E") %>%
  filter( var %in% c("total_accel_belt", "total_accel_arm", "total_accel_dumbbell", "total_accel_forearm" ))


pltChart <- ggplot(dfAux
               ,aes(x=ts, y=val, color=var)) +
    geom_point(shape=20) +
    facet_grid( user_name ~ . )

# pltChart
```


### featurePlot

```{r echo=TRUE}
featurePlot( x = dfTrain_X %>%
               select(-user_name 
                      , -raw_timestamp_part_1, -raw_timestamp_part_2
                      )
            ,y = dfTrain_Y$classe
            ,plot = "box"
)
#                      , -raw_timestamp_part_1, -raw_timestamp_part_2
```



## Pre-Processing

### Zero and Near-Zero variability, and correlation between predictors

Zero and Near-Zero variability variables:
```{r echo=FALSE}
nzv <- nearZeroVar(dfTrain_X, saveMetrics= TRUE)
nzv %>% rownames_to_column(var = "col") %>% filter(zeroVar == TRUE |  nzv == TRUE)
```

```{r echo=FALSE}
# Correlated
comboInfo <- findLinearCombos(dfTrain_X %>% select(-user_name))

comboInfo

# High Corr
corClean <-  cor(dfTrain_X %>% select(-user_name))
# summary(corClean[upper.tri(corClean)])

cutoff <- 0.75

highCorr <- sum(abs(corClean[upper.tri(corClean)]) > cutoff)

vHighlyCor <- findCorrelation(corClean, cutoff = cutoff, names=FALSE, exact=TRUE)

vNames_HighlyCor <- findCorrelation(corClean, cutoff = cutoff, names=TRUE, exact=TRUE)

# names(dfTrain_X)[vHighlyCor]

# we keep hi-correlated vars because will use PCA, so correlation will not be a problem


```

Variables to be ommited because of linear correlation:
```{r echo=FALSE}
vNames_HighlyCor
```


PCA transformation seems to emphasize the difference between users instead of difference wetween classes.


```{r echo=FALSE}
lstPca <- prcomp(dfTrain_X %>% select(-user_name),
                 center = TRUE,
                 scale. = TRUE) 

# plot(lstPca, type = "l")

dfPca <- as_tibble(lstPca$x)

trans = preProcess(dfTrain_X %>% select(-user_name), 
                   method=c("center", 
                            "scale", "pca"))
dfPC = predict(trans, dfTrain_X %>% select(-user_name))

pltClasse <- qplot(x = PC1, y=PC2, shape=dfTrain_Y$correct
      ,color = dfTrain_Y$classe
      ,alpha = 0.25
      ,data=dfPC
      )

pltUser <- qplot(x = PC1, y=PC2, shape=dfTrain_Y$correct
      ,color = dfTrain_X$user_name
      ,alpha = 0.25
      ,data=dfPC
      )

# pltClasse34 <- qplot(x = PC3, y=PC4, shape=dfTrain_Y$correct
#       ,color = dfTrain_Y$classe
#       ,alpha = 0.25
#       ,data=dfPC
#       )
# 
# pltUser34 <- qplot(x = PC3, y=PC4, shape=dfTrain_Y$correct
#       ,color = dfTrain_X$user_name
#       ,alpha = 0.25
#       ,data=dfPC
#       )

grid.arrange(pltClasse, pltUser, ncol = 1)
```



## Cross-validation

```{r echo=FALSE}
nFolds <- 8

folds <- createFolds(dfTrain_Y$correct, k = nFolds) 

ctrlFolds <- trainControl( method = "cv"
                           ,number = nFolds
                           ,classProbs = TRUE
                           ,index = folds
                           )
```




## Models

```{r echo=FALSE}
# dfTrain_XY <- dfPC %>% 
#   mutate(correct = dfTrain$correct)

dfTrain_XY <- dfTrain_X %>% 
  select(-vNames_HighlyCor) %>% 
  mutate(correct = dfTrain_Y$correct)

```



### Model Random Forest
```{r eval=FALSE, echo=FALSE}
cl <- makePSOCKcluster(4)

registerDoParallel(cl)

set.seed(33833)
system.time(mdlRF <- train( correct ~ .
             , method="rf"
             , trControl = ctrlFolds
             , data=dfTrain_XY))

stopCluster(cl)


mdlRF
```


  >    user  system elapsed 
  >   43.64    0.44   88.46 
  > Random Forest 
  > 
  > 19216 samples
  >    35 predictor
  >     2 classes: 'No', 'Yes' 
  > 
  > No pre-processing
  > Resampling: Cross-Validated (8 fold) 
  > Summary of sample sizes: 2403, 2402, 2402, 2402, 2402, 2401, ... 
  > Resampling results across tuning parameters:
  > 
  >   mtry  Accuracy   Kappa    
  >    2    0.9859938  0.9651365
  >   20    0.9932125  0.9832885
  >   39    0.9887074  0.9720965
  > 
  > Accuracy was used to select the optimal model using the largest value.
  > The final value used for the model was mtry = 20.
  > 


### Model GLM
```{r echo=FALSE}
set.seed(7581)
system.time(mdlGLM <- train( correct ~ .
             , method="glm"
             , trControl = ctrlFolds
             , data=dfTrain_XY))

mdlGLM
```


* Note:
    * We will accept the model even with several warnings on potential colinearity since:
        * we droped variables with high correlation
        * the cross-validation accuracy is still high
    * So we migth have overfitting (or perfect predictions) on some cases but not in a scale that invalidate the prediction
    * On the other hand, we have 2402 cros-valitation test cases for 35 predictors, so we bet most likely it's a good prediction and not overfitting.
    * The same goes for LDA
    

### Model GBM
```{r echo=FALSE}
set.seed(7581)
system.time(mdlGBM <- train( correct ~ .
             , method="gbm"
             , trControl = ctrlFolds
             , data=dfTrain_XY))

mdlGBM
```




### Model LDA
```{r echo=FALSE}
set.seed(7581)
system.time(mdlLDA <- train( correct ~ .
             , method="lda"
             , trControl = ctrlFolds
             , data=dfTrain_XY))

mdlLDA
```


### Model Stacked
```{r echo=TRUE}
vTrainGLM <- predict(mdlGLM,  dfTrain_XY)
vTrainLDA <- predict(mdlLDA, dfTrain_XY)

vTrainGBM <- predict(mdlGBM, dfTrain_XY)

# comparing bothe predictions
# confusionMatrix(vTrainGLM, vTrainLDA)
# confusionMatrix(vTrainGLM, vTrainGBM)
# confusionMatrix(vTrainLDA, vTrainGBM)

dfStacked_Train <- tibble( correct = dfTrain_XY$correct
                           ,user_name = dfTrain_XY$user_name
                           ,glm = vTrainGLM
                           ,lda = vTrainLDA
                           ,gbm = vTrainGBM
)
```



```{r echo=TRUE}
cl <- makePSOCKcluster(4)

registerDoParallel(cl)

set.seed(33833)
system.time(mdlStacked <- train(correct ~ .
                    , method="rf"
                    , trControl = ctrlFolds
                    , data=dfStacked_Train))

stopCluster(cl)


mdlStacked

```



## Apply to Test

```{r echo=FALSE}

lvl <- levels(dfTrain_XY$user_name)

vTest_cols <- setdiff( names(dfTrain_XY), c("correct","problem_id" ))
dfTest <- dfTest_Read %>% 
  select(vTest_cols) %>% 
  mutate( user_name = factor(user_name, levels = lvl))
  
```


Prediction:
* Yes :  correcto (classe "A")
* No : incorrect

```{r echo=TRUE}
vTestGLM <- predict(mdlGLM,  dfTest)
vTestLDA <- predict(mdlLDA, dfTest)

vTestGBM <- predict(mdlGBM, dfTest)

dfStacked_Test <- tibble(   user_name = dfTest$user_name
                           ,glm = vTestGLM
                           ,lda = vTestLDA
                           ,gbm = vTestGBM
)


vTest_Stacked <- predict(mdlStacked, dfStacked_Test)

dfStacked_TestXY <- dfStacked_Test %>%
  mutate(result = vTest_Stacked)

dfResult <- dfTest %>%
  mutate(problem_id = dfTest_Read$problem_id
         ,prediction = vTest_Stacked
         ) %>%
  select(problem_id, prediction
         ,user_name, num_window
         )
dfResult
```

